The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
summer and winter

### Network types and construction
We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
individual nodes and two aspects (season and landcover). Two season
elementary-layers (winter and summer) and three landcover elementary-layers
(forest, forage, and open) combined for a total of six layers. Layers were
composed of individuals represented as nodes and social associations represented
as edges, for each season and landcover combination. Proximity-based social
network layers were generated using the R package `spatsoc` [@Robitaille_2019]
in `r version$version.string` [@R_Core_Team_2019].
<!-- TODO: FIX VANDER WAL IN SPATSOC REF -->

@@

(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.  Individual caribou (n = `r DT[, uniqueN(get(idcol))]`) are show as nodes and each indiviual is represented by a unique color. Six layers represent combinations of two seasons (winter and summer) and three habitat classes (open, forest and forage). Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI). Interlayer edges connect individuals to themselves across seasons and within habitat classes (e.g. individual "A" in summer, forest and individual "A" in winter, forest).

@@

Increasing landcover resolution resulted in a decreased proportion of forage, a
rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats. Mean graph strength increased consistently in winter forest and
open habitats. Mean graph strength in winter forage varied across landcover
resolutions with an increase at 250 m and decrease at 500 m. Individuals in
summer layers had consistent weak connections. Layer relevance was stable in
winter for open and forest habitats but decreased for forage habitats (Figure
\@ref(fig:lcres)b). Layer relevance was stable for all habitat classes in summer
layers. Layer similarity was stable for forest and open, except for a sharp
decrease in layer similarity in open at 100 m and 250 m (Figure
\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
winter and summer forage because, at all landcover resolutions greater than 30
m, there were no individuals connected in the network layers. Individuals still
used forage habitats but given a lower availability due to increasing landcover
resolution, at a much lower rate. Connective redundancy slightly decreased as
landcover resolution increased (Figure \@ref(fig:lcres)d). These results
indicate the importance of matching landcover resolution to scale of selection
as well as ensuring the landcover product used has a resolution fine enough to
detect landscape features and habitats relevant to study species.

>>>>

### Network types and construction
We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
individual nodes and two aspects (season and landcover). Two season
elementary-layers (summer and winter) and three landcover elementary-layers
(forest, forage, and open) combined for a total of six layers. Single layers were
composed of individuals lnked by social associations, for each season and landcover combination. Proximity-based social
network layers were generated using the R package `spatsoc` [@Robitaille_2019]
in `r version$version.string` [@R_Core_Team_2019].
<!-- TODO: FIX VANDER WAL IN SPATSOC REF -->

@@

(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.  Individual caribou (n = `r DT[, uniqueN(get(idcol))]`) are show as nodes and each indiviual is represented by a unique color. Six layers represent combinations of two seasons (summer and winter) and three habitat classes (open, forest and forage). Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI). Interlayer edges connect individuals to themselves across seasons and within habitat classes (e.g. individual "A" in summer, forest and individual "A" in winter, forest).

@@

Increasing landcover resolution resulted in a decreased proportion of forage, a
rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats. Mean graph strength increased consistently in winter forest and
open habitats. Mean graph strength in winter forage varied across landcover
resolutions with an increase at 250 m and decrease at 500 m. Individuals in
summer layers had consistent weak connections. Layer relevance was stable in
winter for open and forest habitats but decreased for forage habitats (Figure
\@ref(fig:lcres)b). Layer relevance was stable for all habitat classes in summer
layers. Layer similarity was stable for forest and open, except for a sharp
decrease in layer similarity in open at 100 m and 250 m (Figure
\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
summer and winter forage because, at all landcover resolutions greater than 30
m, there were no individuals connected in the network layers. Individuals still
used forage habitats but given a lower availability due to increasing landcover
resolution, at a much lower rate. Connective redundancy slightly decreased as
landcover resolution increased (Figure \@ref(fig:lcres)d). These results
indicate the importance of matching landcover resolution to scale of selection
as well as ensuring the landcover product used has a resolution fine enough to
detect landscape features and habitats relevant to study species.
